Initial Analysis

### 2019-05-28 Initial_Analysis.Rmd
Ran neighbours list and fixed parallel to run in both windows and mac

## Functions

### Function `EstNeighbors`

@@

```{r funEstNeighbors, eval = T, echo=T}
# Determine which countries are neighbors

@@

  # Get the list using the poly2nb function
  Neighbor_List <- poly2nb(Shapefile)

@@

  # Get the names of the countries for identifying them
  Country_Names <- data_frame(id = row.names(Shapefile@data),
                              Country_Territory = as.character(Shapefile@data$Name),
                              Neighbor_Territory = Country_Territory,
                              EEZID = Shapefile@data$EEZID
                              )

@@

@@

  # Get the index for testing
  Index_EEZ <- Neighbors %>% 
    select(INDEX)

  # Estimate total spp distribution within neighbours
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Index_EEZ$INDEX) %>% 
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)) %>% 
    filter(Model_Index > 0) %>% 
    mutate(Model_Index = Model_Index*100) %>% 
    left_join(Neighbors,
              by = "INDEX")

@@

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
#The File
fnam_world <- "SAUEEZ_July2015.shp"
#Load it!

@@

## Species Test Data Just to know what's captured in these countries
#
# SAU_Data <- fread("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Catch_Data_Test/SAU_Catch_Data_Test.csv")
# #
# # #### Species per country
# #
# Spps <- SAU_Data %>%
#   filter(data_layer == "Reconstructed domestic catch") %>%
#   group_by(area_name,TaxonName = scientific_name) %>%
#   summarise(n()) %>%
#   left_join(Exploited_Species,
#             by = "TaxonName") %>%
#   filter(TaxonKey %in% Exploited_Species_List$TaxonKey)
#
# Exploited_Species_List <- Spps$TaxonKey

# Exploited_Species_List <- c(600004,"600006",600107)
# Exploited_Species_List = 600006
# TaxonKey <- unique(Spps$TaxonKey)

```{r Routine, eval = F, echo = F}

# Step 1; EstNeighbordList 
Neighbor_List <- EstNeighbors(Test)
# Neighbor_List <- EstNeighbors(World_EEZs)
# head(Neighbor_List)

# Step 2; EstTransIndex 
system.time(
  Spp_Trans <- bind_rows(
    lapply(
      Exploited_Species_List, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Model = "All", Neighbors = Neighbor_List
    )
  )
)

@@

# Step 1; EstNeighbordList 
Neighbor_List <- EstNeighbors(World_EEZs)
# head(Neighbor_List)

# Check number of cores
n_Cores <- detectCores()
n_Cores

@@

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List[1], FUN=EstTransIndex, Model = "All", Neighbors = Neighbor_List, mc.cores = n_Cores
    )
  )
)

>>>>

## Sub Routine Estimating Neighbords

### Functions `EstNeighbors`

@@

```{r funEstNeighbors, eval = F, echo=T}
# Determine which countries are neighbors

@@

  # Get the list using the poly2nb function

  Neighbor_List <- poly2nb(Shapefile)

@@

  # Get the names of the countries for identifying them
  Country_Names <- tibble(id = row.names(Shapefile@data),
                              Country_Territory = as.character(Shapefile@data$Name),
                              Neighbor_Territory = Country_Territory,
                              EEZID = Shapefile@data$EEZID # specific of SAU sf
                              )

@@

## Sub Routine

```{r Neighbords_Control_Pannel, eval = F, echo = F}

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
#The File
fnam_world <- "SAUEEZ_July2015.shp"
#Load it!

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  Neighbor_List <- EstNeighbors(World_EEZs)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

write.csv(Neighbor_List,
          paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""),
          row.names = F)

@@

    # Estimate total spp distribution within neighbours
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbors$INDEX) %>% # Filter data only located within EEZs
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)) %>% 
    filter(Model_Index > 0) %>% 
    mutate(Model_Index = Model_Index*100) %>% 
    left_join(Neighbors,
              by = "INDEX")

@@

```{r Mclapply_Hack_Fun, eval= T , echo = T, warning = F, message = F}

# The hack
# https://www.r-bloggers.com/implementing-mclapply-on-windows-a-primer-on-embarrassingly-parallel-computation-on-multicore-systems-with-r/

Mclapply_Hack <- function(...){
    ## Create a cluster
    size.of.list <- length(list(...)[[1]])
    cl <- makeCluster(min(size.of.list, detectCores()))

  ## Find out the names of the loaded packages 
    loaded.package.names <- c(
        ## Base packages
        sessionInfo()$basePkgs,
        ## Additional packages
        names(sessionInfo()$otherPkgs))
    tryCatch( {

       ## Copy over all of the objects within scope to
       ## all clusters. 
       this.env <- environment()
       while( identical( this.env, globalenv() ) == FALSE ) {
           clusterExport(cl,
                         ls(all.names=TRUE, env=this.env),
                         envir=this.env)
           this.env <- parent.env(environment())
       }
       clusterExport(cl,
                     ls(all.names=TRUE, env=globalenv()),
                     envir=globalenv())

       ## Load the libraries on all the clusters
       ## N.B. length(cl) returns the number of clusters
       parLapply( cl, 1:length(cl), function(xx){
           lapply(loaded.package.names, function(yy) {
               require(yy , character.only=TRUE)})
       })

       ## Run the lapply in parallel 
       return( parLapply( cl, ...) )
    }, finally = {        
       ## Stop the cluster
       stopCluster(cl)
    })
}

## Warn the user if they are using Windows
if( Sys.info()[['sysname']] == 'Windows' ){
    message(paste(
      "\n", 
      "   *** Microsoft Windows detected ***\n",
      "   \n",
      "   For technical reasons, the MS Windows version of mclapply()\n",
      "   is implemented as a serial function instead of a parallel\n",
      "   function.",
      "   \n\n",
      "   As a quick hack, we replace this serial version of mclapply()\n",
      "   with a wrapper to parLapply() for this R session. Please see\n\n",
      "     http://www.stat.cmu.edu/~nmv/2014/07/14/implementing-mclapply-on-windows \n\n",
      "   for details.\n\n"))
}

## If the OS is Windows, set mclapply to the
## the hackish version. Otherwise, leave the
## definition alone. 
mclapply <- switch( Sys.info()[['sysname']],
   Windows = {Mclapply_Hack}, 
   Linux   = {mclapply},
   Darwin  = {mclapply})

## end mclapply.hack.R

@@

@@

# Load neighbours data from previouse routine
Neighbor_List <- fread(paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""))

####_________________________________________ TESTING PERIOD_________________________________________####
## Species Test Data Just to know what's captured in these countries
#
# SAU_Data <- fread("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Catch_Data_Test/SAU_Catch_Data_Test.csv")
# #
# # #### Species per country
# #
# Spps <- SAU_Data %>%
#   filter(data_layer == "Reconstructed domestic catch") %>%
#   group_by(area_name,TaxonName = scientific_name) %>%
#   summarise(n()) %>%
#   left_join(Exploited_Species,
#             by = "TaxonName") %>%
#   filter(TaxonKey %in% Exploited_Species_List$TaxonKey)
#
# Exploited_Species_List <- Spps$TaxonKey

# Exploited_Species_List <- c("600006",600107)
# Exploited_Species_List = 600107
# TaxonKey <- unique(Spps$TaxonKey)

@@

@@

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List[1], fun =EstTransIndex, Model = "All", Neighbors = Neighbor_List
    )
  )
)

# u ser  system elapsed 
# 72.20    9.33   91.30
